\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-14 public/paper/pyg4ometry.tex
hyphenate time-consuming

{\em Nature of problem(approx. 50-250 words):}\\
Creating computer readable geometry descriptions for Monte Carlo radiation transport (MCRT) codes is a time consuming and error-prone task. 
Typically these geometries are written by the user directly in the file format used by the MCRT code. There are also multiple MCRT codes 
available and geometry conversion is difficult or impossible to convert between these simulation tools. 
\\
{\em Solution method(approx. 50-250 words):}\\
Create a Python application programming interface to read and write files of and process the geometry objects and specification 
language used by Geant4 and FLUKA. Form triangular meshes to represent geometrical objects for both visualisation of the 
geometry and advanced approximate geometrical algorithms. Triangular mesh process allows the loading and use of STL and CAD/CAM 
files. Converting from FLUKA to Geant4 requires algorithms to decompose solids to a set of unions of convex solids. Converting from 
FLUKA to Geant4 requires the replacement of infinite surfaces with finite solids.

@@

%% main text
\section{Introduction} \label{sec:introduction}
There are numerous different software codes to simulate the passage of particles through material radiation transport (RT) programmes these 
include MCNP \cite{Mcnp_Werner}, FLUKA \cite{Fluka_Ferrari,Fluka_Bohlen}, Geant3 \cite{Geant3_Brun} and Geant4 \cite{Geant4_Agostinelli}. 
All these codes are based on the Monte Carlo technique but each code either has a particular specialism, simulation methodology or target user community.  
RT Monte Carlo (RTMC) simulations have diverse uses including shielding calculations for radiological protection, detector performance, medical imaging and therapy and space radiation environment  simulation are some examples. A fundamental requirement of all of the codes is to supply a computer-readable description of the 
physical three-dimensional geometry that  the particles are passing through.  The creation of geometry files is typically a very time consuming 
activity and the simulation validity and performance is directly dependent on the quality of the geometry. There is not general format for geometry for MCRT 
codes and each code will have a specialist format. The requirement of a geometry system that allows the conversion between files prepared for different 
codes will enable cross-checks of the physics processes in different particle transport codes. Typically a MCRT code user will not have geometry in FLUKA 
and Geant4 for example. The file formats used for geometry are typically focused on the computational efficiency of a particle tracking task and not ease of use of a user. In addition to the creation of geometry files for RT programs, usually computer assisted design (CAD) files exist for systems which 
need to be simulated. The fundamental geometric representations in CAD files is typically not amenable for MCRT programs.  For these reasons it is 
advantageous to create a software tool that allows particle transport code users to rapidly develop error-free geometry files, convert between common MCRT 
program geometry formats and finally import CAD models.

>>>>

{\em Nature of problem(approx. 50-250 words):}\\
Creating computer readable geometry descriptions for Monte Carlo radiation transport (MCRT) codes is a time-consuming and error-prone task. 
Typically these geometries are written by the user directly in the file format used by the MCRT code. There are also multiple MCRT codes 
available and geometry conversion is difficult or impossible to convert between these simulation tools. 
\\
{\em Solution method(approx. 50-250 words):}\\
Create a Python application programming interface to read and write files of and process the geometry objects and specification 
language used by Geant4 and FLUKA. Form triangular meshes to represent geometrical objects for both visualisation of the 
geometry and advanced approximate geometrical algorithms. Triangular mesh process allows the loading and use of STL and CAD/CAM 
files. Converting from FLUKA to Geant4 requires algorithms to decompose solids to a set of unions of convex solids. Converting from 
FLUKA to Geant4 requires the replacement of infinite surfaces with finite solids.

@@

%% main text
\section{Introduction} \label{sec:introduction}
There are numerous different software codes to simulate the passage of particles through material radiation transport (RT) programmes these 
include MCNP \cite{Mcnp_Werner}, FLUKA \cite{Fluka_Ferrari,Fluka_Bohlen}, Geant3 \cite{Geant3_Brun} and Geant4 \cite{Geant4_Agostinelli}. 
All these codes are based on the Monte Carlo technique but each code either has a particular specialism, simulation methodology or target user community.  
RT Monte Carlo (RTMC) simulations have diverse uses including shielding calculations for radiological protection, detector performance, medical imaging and therapy and space radiation environment  simulation are some examples. A fundamental requirement of all of the codes is to supply a computer-readable description of the 
physical three-dimensional geometry that  the particles are passing through.  The creation of geometry files is typically a very time-consuming 
activity and the simulation validity and performance is directly dependent on the quality of the geometry. There is not general format for geometry for MCRT 
codes and each code will have a specialist format. The requirement of a geometry system that allows the conversion between files prepared for different 
codes will enable cross-checks of the physics processes in different particle transport codes. Typically a MCRT code user will not have geometry in FLUKA 
and Geant4 for example. The file formats used for geometry are typically focused on the computational efficiency of a particle tracking task and not ease of use of a user. In addition to the creation of geometry files for RT programs, usually computer assisted design (CAD) files exist for systems which 
need to be simulated. The fundamental geometric representations in CAD files is typically not amenable for MCRT programs.  For these reasons it is 
advantageous to create a software tool that allows particle transport code users to rapidly develop error-free geometry files, convert between common MCRT 
program geometry formats and finally import CAD models.
